---
title: "trial Report"
author: "Esha Bandyopadhyay"
date: "January 12, 2019"
output: 
 html_document:
  toc : TRUE
  number_section : TRUE
  highlight : espresso
  fig_caption : yes
  
 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Initial_analysis
## reading in data on PloS papers

```{r read_data, results='hide', message=FALSE}

library(tidyverse)
count_raw <- read_delim("data/counts-raw.txt.gz",delim = "\t")



```


##Diagnostic plots

```{r histogram_weeks_since_pub, fig.width=5, fig.height=3, fig.cap="Figure 1 : weeks since publication per paper"}

weeks_since_pub <- count_raw$daysSincePublished/7
hist(weeks_since_pub, xlab="# of weeks", main = "weeks since publication")


```

## some vague statements about the data

Here is an example of a mathematical function : $y = x^2$

This dataset consists of `r dim(count_raw)[1]` publications

<!-- Turns out my data was notgood -->

```{r scatterplot_pubs_vs_citations}

plot(count_raw$daysSincePublished, count_raw$wosCountThru2011)

```

```{r analysis of x and plot it both histogram and scatter plot}

x <- count_raw$mendeleyReadersCount
hist(x, breaks =  100, xlab="mendeley readers", main = "readers")

plot(count_raw$mendeleyReadersCount, count_raw$wasCountThru2011, xlab="readers", ylab="citations in 2011", main="mendeley readers vs citations")

```

### A quick refresher on functions in `R`


```{r}
count_raw[,"authorsCount"]
count_raw[["authorsCount"]]
data <- count_raw$authorsCount
plot(x = count_raw$wosCountThru2011,y=data)
data_column <- "deliciousCount"
data <- count_raw[[data_column]]
log_data <-log(data)
plot(x = count_raw$wosCountThru2011,y=log_data)
```


```{r}
log_data <- function(input_dataframe,column){
  data_column <- input_dataframe[[column]]
  log_data_column <- log(data_column)
  return(log_data_column)
}
output <- log_data(input_dataframe = count_raw,
         column = "deliciousCount")
plot(x = count_raw$authorsCount,y=output)
```

```{r}
publication_date <-count_raw$pubDate
head(publication_date)
num_unique <- function(x){
  unique_data <- unique(x)
  length_unique <- length(unique_data)
  return(length_unique)
}
debug(num_unique)
num_unique(x = count_raw$pubDate)
```

```{r}
column_num_unique <- function(data,column_name){
  data_column <- data[[column_name]]
  if(is.null(data_column)){
    stop("No such column in data!")
  }
  unique_entries <- num_unique(data_column)
  return(unique_entries)
}
debug(column_num_unique)
column_num_unique(data = count_raw,column_name = "doi")
```

### For loops and for fun


```{r}
fake_fun <- function(){
 x <- 4 
  
  
}
```


```{r}
names_of_columns <- colnames(count_raw)
my_column <- "doi"
column_num_unique(data = count_raw,
                  column_name = my_column)
unique_col_ct <- function(data){
  data_column_names <- colnames(data)
  output_length <- length(data_column_names)
  result <- integer(output_length)
  for(i in seq_along(data_column_names)){
    my_column <- data_column_names[i]
    result[i] <- column_num_unique(data,my_column)
  }
  print("we finished!")
  return(result)
}
debug(unique_col_ct)
doy_cols <- which(colnames(count_raw)=="doy")
unique_col_ct(count_raw[,doy_cols])
```


```{r}
counts_columns <- c("facebookShareCount",
                    "facebookLikeCount")
max_of_each_col <- function(data,count_colnames){
  number_of_columns <- length(count_colnames)
  result <- integer(number_of_columns)
  for(i in seq_along(count_colnames)){
    my_column <- count_colnames[i]
    my_vector <- data[[my_column]]
    result[i] <- max(my_vector)
  }
  return(result)
}
debug(max_of_each_col)
max_of_each_col(count_raw,counts_columns)
```


## Quick refresher on subsetting with R

There are many ways to subset data in R
### We can subset a vecter by position with `[`
```{r}
x <- c(8,9,3,5,7)
x[4]
y <- c(1,2)
x[y]
z <- length(x)
x[z]
```
We can also subset using double bracket syntax
to get *one* element back
##```{r}
x[[1]]
x[[y]]
##```
## Indexing dataframes
Dataframes can also be indexed with single bracket `[` and double bracket `[[` syntax depending on what we want

```{r}
count_raw[,1]
y <- c(1,2)
count_raw[,y]
count_raw[,c("doi","daysSincePublished")]
(count_vector <- count_raw[["doi"]])
(doi_dataframe <- count_raw[,"doi"])
```


